Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
Discuss k contours

% Compare contours of TKE for 2 simulation cases and experiments
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering

>>>>

Turbulence kinetic energy contours for the experimental measurements and each
CFD case at $x/D=1$ are presented in Figure~\ref{fig:kcont}. As seen in the
profiles in Figure\ref{fig:profiles}, the SA model is resolving very little of
the flow unsteadiness. In contrast, the SST model does a good job predicting the
locations and magnitudes of various peaks in $k$. These are generated along the
top of the turbine via tip vortex shedding, and the $-y$ side of the turbine via
dynamic stall. We do however see the smearing effect from the dynamic stall
vortex centered around $z/H=0$, which is likely more of an issue with wake
evolution rather than wake generation.
